### 2014-09-05 relax2.tex
intro

\section{Exploration of Unexecuted Branches}~\label{sec:relax2}
We now switch to the second feature of \tool, which is its ability to reason about neighboring branches that are not executed in the original trace $\tau$.
At the high level, we replace the constraints that model the executed branch to the constraints that conservatively model the possible executions in both branches.
We leverage the static analysis to  realize this relaxation. We explain the details below.

As the static analysis has some known challenges, we make several simplifying assumptions: (1) the branch structure does not contain loops or recursions; (2) every base reference variables can be fully resolved to a concrete object, as required by our analysis (Section~\ref{sec:relax1}).
% If the base reference variable is defined out of the branch and is not updated inside the unexplored branch, it is resolved to the object referenced by the variable at the beginning of the branch, which is computed from the trace. If the base reference variable is updated inside the unexplored branch to some shared access, the base reference variables cannot be fully resolved statically. However, if it is updated to an object created inside the unexplored branch, we can still model the object and treats the variable as fully resolved.
 (3) we assume there are no array accesses in the branch structure, because the array accesses often use the index expressions that cannot be fully resolved statically. Similarly, we assume there are no use of collections. If any of the above assumptions is violated, we  avoid exploring the unexplored branches and adopt the purely dynamic solution in Section~\ref[sec:relax1}. 
 %TODO inline

>>>>

\section{Exploration of Unexecuted Branches}~\label{sec:relax2}
We now switch to the second feature of \tool, which is its ability to reason about neighboring branches that are not executed in the original trace $\tau$.
At the high level, we replace the constraints that model the executed branch to the constraints that conservatively model the possible executions in both branches.
We leverage the static analysis to  realize this relaxation.

We start with a branch event in the trace, without loss of generality, suppose its true branch is taken, we need to explore the false branch and add constraints to model it. As the static analysis has some known challenges, we make several simplifying assumptions: (1) the unexplored branch should not contain loops or recursions because the loop bound may depend on some shared variable which is statically unknown; (2) every base reference variable should be fully resolved to a concrete object, as required by our analysis (Section~\ref{sec:relax1}). We apply dataflow analysis (reaching definitions) to judge: If the base reference depends on some shared read in the explored branch, of which the value is statically unknown, it cannot be statically resolved to an object; If the base reference depends on multiple definitions from different paths, it cannot be statically resolved to an object. Otherwise, it can be resolved. (3) We assume the unexplored branch does not contain array access because the array accesses often use the index expressions that are statically unknown. Similarly, as the collections often use array for implementation, we assume they are also absent. (4) We inline the method calls (for two levels) in the unexplored branch, similar to the base object, we assume the caller object can be fully resolved statically.  If any of the above assumptions is violated, we  avoid exploring the unexplored branches and adopt the purely dynamic solution in Section~\ref[sec:relax1}. 
We use the example in Figure~\ref{fig:running2}
